Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-24 paper/paper.tex
another pass on technique overview

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, which is
provided on input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects rule options directly from the input messages (see
Section~\ref{sec:rules-and-packets}). As only malicious traffic is
considered in this step, the rule produced is likely overspecified,
\ie{}, it may be more restrictive than the golden rule (see
Section~\ref{sec:suri-metas-coverage}). Consequently, the use of that
rule could lead to false negatives. Second, \tname{} generates rules
that weakens the constraints expressed in the inferred seed rule
whilest still capturing the malicious traffic. Given that every option
declared in a rule needs to be satisfied for a rule to capture an
attack, any subset of the set of options---inferred in the first
step---captures the malicious traffic by definition. \tname{}
leverages that observation to search for rules containing a proper
subset of rules defined in the original seed option. Although that
approach captures the malicious traffic, it can result in false
positives. Intuitively, there are no restrictions on to what extent a
rule can be relaxed. \tname{} uses benign traffic for that
purpose. The minimization step uses a population-based gradient
descent-like search to find all plausible rules derived from the seed
rule, obtained in the previous step. Finally, \tname{} uses several
heuristic functions derived from a data set of existing rules to rank
the plausible rules generated in the previous step.

>>>>

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, which is
provided on input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects options directly from the input messages (see
Section~\ref{sec:rules-and-packets}). More precisely, it produces a
rule containing all possible options satisfied by the traffic. Let us
refer to that rule as the \emph{seed rule} and its corresponding set
of options as \emph{seed options}. Note that, as only malicious
traffic is considered in this step, the seed rule is likely
overspecified, \ie{}, it may be more restrictive than the golden rule
(see Section~\ref{sec:suri-metas-coverage}). Consequently, the use of
that rule to capture attacks associated with the input traffic could
lead to false negatives.  Second, \tname\ generates rules that weaken
the constraints associated with the seed options whilst still
capturing the malicious traffic. Given that every option declared in a
rule needs to be satisfied for a rule to capture an attack, any subset
of the set of seed options must capture the malicious traffic by
definition. \tname{} leverages that observation to search for rules
containing a proper subset of options from the seed options. However,
note that that approach alone could result in false positives as it
imposes no limit on to what extent a rule can be relaxed. \tname{}
uses benign traffic for that purpose. More precisely, it uses a
gradient descent-like search to find all plausible rules derived from
the seed rule, obtained in the previous step. Finally, \tname{} uses
several heuristic functions derived from a data set of existing rules
to rank the plausible rules generated in the previous step by their
similarity to existing rules. The rationale is that many plausible
rules can be generated in this step and they have different semantics,
which can differ from user's intent. Similarity is used to approximate
user's intent.
